A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-23 paper.tex
3d section

Let $\{s^1_+, s_+^2\}$ be a basis for $S_+^4$. 
We twist by a supercharge of the form
\[
Q_t = s_+^1 \otimes u \otimes \alpha_+ + t s_+^2 \otimes v \otimes \alpha_+
\]
where $t \in \CC$. 
When $t \ne 0$, this supercharge is of rank $(2,0)$. 
At $t = 0$ it reduces to the holomorphic supercharge from the previous section.

@@

\begin{prop}
Suppose $Q_t$ is the rank $(2,0)$ supercharge as above.
The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
\begin{align*}
I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) \right) \\
I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac 14 t (\psi^*, \psi^*)
\end{align*}
\end{prop}
\begin{proof}
We first write down the fields and the functionals in $\Spin(4)$-notation.
The fields of $4d \cN=2$ decompose as:
\begin{itemize}
 \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(a \otimes \alpha_-^{\otimes 2} ,\Tilde{a} \otimes \alpha_+^{\otimes 2}) \in \Omega^0(\RR^4; (S^2_-)^{\otimes 2} \otimes \gg \oplus  (S^2_-)^{\otimes 2} \otimes \gg)$.
  \item $\gg$-valued fermions: a $W = W_+ \otimes S_+^2$-valued Dirac spinor $\lambda = (\lambda_+ \otimes \alpha_+, \lambda_-\otimes \alpha_-) \in \Omega^0(\RR^4; (S^4_+ \otimes W \oplus S^4_- \otimes W^*) \otimes \gg)$.
 \item $U$-valued bosons: a $W = W_+ \otimes S_+^2$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W_+ \otimes S_+^2 \otimes U)$.
 \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+ \otimes \alpha_- ,\psi_- \otimes \alpha_+) \in \Omega^0(\RR^4; (S^4_+ \otimes S_-^2 \oplus S^4_- \otimes S_+^2) \otimes U)$.
 \item a ghost $c \in \Omega^0(\RR^4 ; \gg)$.
\end{itemize}
The anti-fields decompose in an analogous way.

@@

\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang-Mills with Hypermultiplet Matter} \label{3d_4_section}
We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
 \item $U$-valued bosons: a $W$-valued scalar field $(\phi \otimes v) \in \Omega^0(\RR^3; W \otimes U)$.
 \item $\gg$-valued fermions: a pair of $W$-valued spinors $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes \gg \otimes (W \oplus W))$.
 \item $U$-valued fermions:  a pair of spinors $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Twisting data:}
In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.  In addition to rank one square-zero supercharges, which sit inside an $\mc N=2$ subalgebra, there are two possible classes of rank two square-zero supercharges.  The corresponding twisted theories are obtained by dimensionally reducing the 4d $\mc N=2$ theory twisted by a rank $(1,1)$, or a rank $(2,0)$ square-zero supercharge.  Let's first discuss the rank 1 twist, and its deformation to a perturbatively trivial rank 2 twist.

\subsubsection{Minimal Twist}

\subsubsection{Topological A Twist}
\begin{theorem} \label{3d_4_holo_A_twist_thm}
The minimal twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U\ham \gg))$. The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U\ham \gg)_{\mr{Hod}})$.
\end{theorem}

\begin{proof}
To prove this, we start with the one-parameter family of 4d twisted theories which we computed Theorem \ref{4d_Donaldson_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to reduce to a one-parameter family of 3d twisted theories.
\end{proof}

\subsubsection{Topological B Twist}

\begin{theorem} \label{3d_2_B_twist_thm}
The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$.  This theory is generally only $\ZZ/2\ZZ$-graded.
\end{theorem}

\begin{proof}
Again, we prove this by dimensional reduction from a 4d $\mc N=2$ twisted theory, in this case the rank $(1,1)$ twist from Theorem \ref{4d_11_twist_thm}, by applying Proposition \ref{CS_diml_red_prop}.
\end{proof}

\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d_8_section}
Finally, let's consider maximal super Yang-Mills theory with gauge group $G$ in dimension 3, with $\mc N=8$ supersymmetry.  This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\mr O(3)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and seven scalar fields $\phi_i \in \Omega^0(\RR^3; \gg)$.
 \item Fermions: eight spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Twisting data:}
The classes of square-zero supercharge in the 3d $\mc N=8$ supersymmetry algebra are categorized in the same way as in the $\mc N=4$ supersymmetry algebra.  There are minimal twisting supercharges of rank 1, and two classes of topological twisting supercharges of rank 2, which we refer to as the A-twist (obtained from a rank $(2,0), (2,1)$ or generic $(2,2)$ supercharge in $4d \mc N=4$), and the B-twist (obtained from a rank $(1,1)$ or special rank $(2,2)$ supercharge in 4d $\mc N=4$).  The twisted theories can be calculated either by dimensional reduction -- by applying Proposition \ref{CS_diml_red_prop} to the theories from Section \ref{4d_4_section}, or from the 3d $\mc N=4$ twists by considering the representation $U = T^*\gg$.

\subsubsection{Minimal Twist}

\subsubsection{Topological A Twist}

\begin{theorem} 
The minimal twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$. The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$.
\end{theorem}

\subsubsection{Topological B Twist}

\begin{theorem} 
The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$. 
\end{theorem}

>>>>

Let $\{s^1_+, s_+^2\}$ be a basis for $S_+^4$. 
We twist by a supercharge of the form
\begin{equation} 
\label{eq:4dHodgefamily}
Q_t = s_+^1 \otimes u \otimes \alpha_+ + t s_+^2 \otimes v \otimes \alpha_+
\end{equation}
where $t \in \CC$. 
When $t \ne 0$, this supercharge is of rank $(2,0)$. 
At $t = 0$ it reduces to the holomorphic supercharge from the previous section.

@@

\begin{prop}
Suppose $Q_t$ is the rank $(2,0)$ supercharge of \ref{eq:4dHodgefamily}.
The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
\begin{align*}
I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) \right) \\
I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac 14 t (\psi^*, \psi^*)
\end{align*}
\end{prop}
\begin{proof}
We first write down the fields and the functionals in $\Spin(4)$-notation.
The fields of $4d \cN=2$ decompose as:
\begin{itemize}
 \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(a \otimes \alpha_-^{\otimes 2} ,\Tilde{a} \otimes \alpha_+^{\otimes 2}) \in \Omega^0(\RR^4; (S^2_-)^{\otimes 2} \otimes \gg \oplus  (S^2_-)^{\otimes 2} \otimes \gg)$.
  \item $\gg$-valued fermions: a $W = W_+ \otimes S_+^2$-valued Dirac spinor $\lambda = (\lambda_+ \otimes \alpha_+, \lambda_-\otimes \alpha_-) \in \Omega^0(\RR^4; (S^4_+ \otimes W \oplus S^4_- \otimes W^*) \otimes \gg)$.
 \item $U$-valued bosons: a $W = W_+ \otimes S_+^2$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W_+ \otimes S_+^2 \otimes U)$.
 \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+ \otimes \alpha_- ,\psi_- \otimes \alpha_+) \in \Omega^0(\RR^4; (S^4_+ \otimes S_-^2 \oplus S^4_- \otimes S_+^2) \otimes U)$.
 \item a ghost $c \in \Omega^0(\RR^4 ; \gg)$.
\end{itemize}
The anti-fields decompose in an analogous way.

@@

\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang-Mills with Hypermultiplet Matter} \label{3d_4_section}
We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.  The $R$-symmetry group is $G_R = \SO(4)$, acting on $W$ by its defining representation. \chris{or should it be $\spin(3;\RR)$?}

In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.  An element $Q \in S \otimes W$ gives rise to a map $S^* \to W$; $Q$ squares to zero if its image is totally isotropic.  The classification of orbits includes the rank of this map.
\begin{itemize}
 \item Rank 1.  In this case $Q$ is minimal, with 2 invariant directions.  Such supercharges come from the $\mc N=2$ supersymmetry algebra.  They admit a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
 \item Rank 2 $A$-twist.  Rank 2 supercharges are topological.  A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore a volume form.  There are two orbits for the $G_R = \SO(4)$ action on the space of volume forms, which we refer to as the $A$-twist and the $B$-twist.  The $A$-twist arises by dimensional reduction from the rank $(2,0)$ twist in 4d.  It admits a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
 \item Rank 2 $B$-twist.  The other topological orbit arises by dimensional reduction from the rank $(1,1)$ twist in 4d.  It admits a twisting homomorphism $\phi \colon \spin(3;\RR) \iso \SU(2) \to \SO(4)$. 
\end{itemize}

We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
 \item $U$-valued bosons: a $W$-valued scalar field $(\phi \otimes v) \in \Omega^0(\RR^3; W \otimes U)$.
 \item $\gg$-valued fermions: a pair of $W$-valued spinors $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes \gg \otimes (W \oplus W))$.
 \item $U$-valued fermions:  a pair of spinors $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
\end{itemize}

\subsubsection{Minimal Twist}
The 3d $\cN=4$ super Yang--Mills viewed as a $\cN=2$ supersymmetric theory coincides with the 3d $\cN=2$ super Yang--Mills with matter valued in the representation $R = U \oplus \gg$. From Theorem \ref{3d_minimal_twist_thm} we obtain the following statement.

\begin{theorem} \label{3d_4_minimal_twist_thm}
The minimal twist of 3d $\cN=4$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U\ham \gg))$. Moreover, the equivalence is $\U(1)$-equivariant.
\end{theorem}

\subsubsection{Topological A Twist}
Let $L=\CC$ equipped with a Hermitian structure and a complex half density, $N_\RR=\RR$ equipped with a Euclidean structure and $N=N_\RR\otimes_\RR\CC$ its complexification. Consider the 4-dimensional spacetime $V_\RR=L\times N$. Under the projection $\Re\colon N\rightarrow N_\RR$ the family $Q_t$ of 4-dimensional square-zero supercharges given by \eqref{eq:4dHodgefamily} dimensionally reduces to a family of 3-dimensional square-zero supercharges which at $t\neq 0$ are topological at and $t=0$ have 2 invariant directions. Since they admit a compatible $\ZZ$-grading, at $t=0$ we obtain the holomorphic twist and at $t\neq 0$ we obtain the topological B twist. Therefore, from Theorem \ref{thm:4dDonaldsontwist} we obtain the following statement.

\begin{thm}
The twist of 3d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U\ham \gg)_{\mr{Hod}})$. Moreover, this equivalence is $\U(1)$-equivariant.
\label{3d_4_A_twist_thm}
\end{thm}

\begin{cor}
The topological $A$ twist of 3d $\cN=4$ super Yang--Mills is perturbatively trivial.
\end{cor}

\subsubsection{Topological B Twist}
We consider $V_\RR=\RR^3$ equipped with a Euclidean structure and as before let $V=V_\RR\otimes_\RR\CC$ be its complexification. $V$ carries a Hermitian structure and a half-density, so by the results of Section \ref{sec:6dholomorphictwist} we obtain a square-zero supercharge $Q$. Under the projection $\Re\colon V\rightarrow V_\RR$ the supercharge $Q$ dimensionally reduces to the topological $B$ supercharge in 3 dimensions. Therefore, from Theorem \ref{thm:6dCSreduction} we obtain the following statement.

\begin{theorem} \label{3d_4_B_twist_thm}
The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$. Moreover, the equivalence is $\Spin(5, \RR)$-equivariant. 
\end{theorem}

\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d_8_section}
Finally, let's consider maximal super Yang-Mills theory with gauge group $G$ in dimension 3, with $\mc N=8$ supersymmetry.  This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.  The $R$-symmetry group is $G_R = \Spin(7;
RR)$, acting on $W$ by its (Dirac) spin representation.

In the $\mc N=8$ supersymmetry algebra the classification of twists is the same as we saw in $\mc N=4$.  That is, there are three classes: 
\begin{itemize}
 \item Rank 1.  In this case $Q$ is minimal, with 2 invariant directions.  Such supercharges come from the $\mc N=2$ supersymmetry algebra.  They admit a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
 \item Rank 2 $A$-twist.  These twists are topological, and come from the $\mc N=4$ supersymmetry algebra.  The $A$-twist arises by dimensional reduction from the rank $(2,0)$ twist in 4d.  It admits a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
 \item Rank 2 $B$-twist.   These twists are topological, and come from the $\mc N=4$ supersymmetry algebra. The $B$ twist arises by dimensional reduction from the rank $(1,1)$ twist in 4d.  It admits a twisting homomorphism $\phi \colon \spin(3;\RR) \iso G_R$.
\end{itemize}

 We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\mr O(3)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and seven scalar fields $\phi_i \in \Omega^0(\RR^3; \gg)$.
 \item Fermions: eight spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$.
\end{itemize}

\subsubsection{Minimal Twist}
The 3d $\cN=8$ super Yang--Mills viewed as an $\cN=4$ supersymmetric theory coincides with the 3d $\cN=4$ super Yang--Mills with matter valued in the representation $U = T^*\gg$. From Theorem \ref{3d_4_minimal_twist_thm} we obtain the following statement.

\begin{theorem} 
The minimal twist of 3d $\cN=8$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$. Moreover, the equivalence is $\U(1)$-equivariant.
\end{theorem}

\subsubsection{Topological A Twist}
From Theorem \ref{3d_4_A_twist_thm} we obtain the following statement.

\begin{theorem} 
The twist of 3d $\cN=8$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$. Moreover, this equivalence is $\U(1)$-equivariant.
\end{theorem}

\subsubsection{Topological B Twist}
From Theorem \ref{3d_4_B_twist_thm} we obtain the following statement.

\begin{theorem} 
The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$. Moreover, this equivalence is $\spin(3;\RR)$-equivariant.
\end{theorem}
